Revisiting Multi-Domain Machine Translation

### 2020-08-28 2020/tacl2020/multidomain.tex
version de travail presque finale

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  \hfill{\footnotesize[65m]} & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Mixed-Bal}   \hfill{\footnotesize[65m]} &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       \hfill{\footnotesize[6$\times$65m]} & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & \SB{42.7} & \SB{53.8} \\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag} \hfill{\footnotesize[+4k]}        & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.6 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat} \hfill{\footnotesize[+140k]}    & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDR}       \hfill{\footnotesize[+1.4m]}    & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} &40.9 & 49.8          \\% & 22.1 \\ 
    \system{TTM}      \hfill{\footnotesize[+4k]}        & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.0 & 49.7     \\% &  23.4 \\
    \system{DM}        \hfill{\footnotesize[+0]}         & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 38.1 & 43.4 \\ % & 22.6\\
    \system{ADM}      \hfill{\footnotesize[+0]}         & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 38.9 & 47.5 \\% & 23.3 \\
    \revision{\system{FT Res}}   \hfill{\footnotesize[+12.4m]}  & 37.3 & \SB{57.9} & \SB{53.9} & 33.8 & \SB{46.7} & \SB{90.2}  & \SB{42.3} & \SB{53.3} \\ % & 20.5\\ \hline
    \system{MDL Res} \hfill{\footnotesize[+12.4m]}    & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.0 & \SB{51.9} \\%  & \SW{21.2} \\
%     \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline \hline
    \system{Mixed-Nat-RNN}  & 36.8 & 53.8 & 47.2 & 30.0 & 35.7 & 60.2  & 39.2  & 44.0 \\
    \hline
    \system{WDCMT}       & 36.0 & 53.3 & \SB{48.8} & 31.1 & \SB{38.8} & \SW{58.5} & 39.0 & 44.4 \\ % & 20.4 \\
    \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems \revision{based on the same Transformer (top) or RNN (bottom) architecture. The former contains 65m parameters, the latter has ???. For each system, we report the number of domain specific parameters,}  BLEU scores for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. \revision{In the former case, we take the domain proportions from Table~\ref{tab:Corpora}}. Boldface denotes significant gains with respect to \system{Mix-Nat} (or \system{Mix-Nat-RNN}, for WDCMT), underline denotes significant losses.}
  \label{tab:performance}
  % \fyDone{Fill the table with all results, including a comparison with *RNNs* for wcmd}
  \fyDone{Do we have significancy tests for averages?} %\fyTodo{Add tests wrt to RNN}
\end{table*}

@@

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{\domain{rnd}} &  \multicolumn{1}{c|}{\domain{new}}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_2$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5} & -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& \SW{-19.6} & \SW{-3.3}\\% [32.5]
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}  & +0.2& -0.4 & -0.4 & -0.5 & -0.4 & \SW{-13.4} & \SW{-1.7}\\% [35.9]
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3}   & +0.3 & +0.3 & +0.3 & 0.3 & +0.1 & \SW{-14.2} &\SW{-1.8}\\ % [34.9] 
    \system{LDR}           & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& \SW{-12} & \SW{-1.4}\\ % [37.0]
    \system{TTM} (*)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & 0.0 & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (*)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & 0.0 &-0.9\\
    \system{ADM} (*)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & 0.0&-0.2\\
    \revision{\system{FT Res}}   & -0.1   & -0.4 & -0.3 &-0.3 & \SW{-2.2} & \SW{-2.9} & \SW{-2.4} & -\SW{3.2} & \SW{-13.3} & \SW{-3.0}\\ % [31.8]
    \system{MDL Res}   & -0.2   & -0.1 & +\SB{0.2} &+0.0 & -0.9 & -0.9 & +0.7 & -0.3 & \SW{-18.6} & \SW{-1.3}\\ % [31.8]
    \system{WDCMT} (*)     & -0.0    & -0.0  & +0.2 & +0.2  & +0.8 & +0.8  & -0.4 & -0.8 & 0.0 & +0.2 \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. In the Split/Merge experiments, we report BLEU differences for the related test set(s). Underline denotes significant loss when domains are changed wrt.\ the baseline situation; bold for a significant improvement over \system{FT-Full}; (*) tags systems ignoring test domains.
    \fyDone{Check wrong and significance of diff for ``old''}\fyDone{How about wrong ?}
  }
  \label{tab:redomains}
\end{table*}

@@

%    \system{WDCMT}     &&&&&&& & &\\[-2pt]
%                    &&&&&&&&& \\
    \footnotesize \revision{\system{FT Res}}  & 37.0 & 57.6 & 53.8 & 34.5 &	46.1 & 91.1 & 29.6 &	42.2  & 53.3 \\[-2pt]
                               & \sbcl{+0.3}{+0.3} & \sbcl{+0.4}{+0.4} & \sbcl{+0.1}{+0.1} & \sbcl{-0.7}{-0.7} & \sbcl{+0.5}{+0.5} & \sbcl{-0.9}{-0.9} & \sbcl{\SW{-9.0}}{-0.6} & \sbcl{-0.1}{-0.1} & \sbcl{+0.2}{+0.2} \\

@@

\subsection{Automatic domains \label{ssec:autodomains}}
In this section, we experiment with automatic domains, obtained by clustering sentences into $k=30$ classes using the k-means algorithm based on generic sentence representations obtained via mean pooling as in Section~\ref{ssec:corpora}. This allows us to evaluate requirement [P7-scale], training and testing our systems as if these domains were fully separated. Many of these clusters are mere splits of the large \domain{med}, while a fewer number of classes are mixtures of two (or more) existing domains \revision{(details are in Appendix B)}. We are thus in a position to reiterate, at a larger scale, the measurements of Section~\ref{ssec:redomains} and test whether multi-domain systems can effectively take advantage from the cross-domain similarities and to eventually perform better than fine-tuning. \revision{Results in Table~\ref{} show that MDMT actually surpass fine-tuning for the smaller clusters, especially for small subsets of the medical domain; for the large clusters, this is no longer true.}

@@

\begin{table*}[t]
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Domain / Model  & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
  %    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
  %     \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
  %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.5 & \SW{54.0} & 49.0   & 33.6 & \SW{42.2} & \SW{76.7} & 41.6 & 49.0 \\%    & 21.8 \\
    \system{DC-Feat}      & 37.3  & 54.2 & 49.3   & 33.6 & \SW{41.9} & \SW{75.8} & 40.8 & \SW{48.7}  \\% & \SW{21.7} \\
    \system{LDR}             & 37.4   & 54.1 & \SW{48.7} & \SW{32.5} & \SW{41.4} & \SW{75.9} & 39.1 & \SW{48.3}         \\% & 22.1 \\ 
    \system{TTM}            & 37.4 & \SW{53.7} & 48.9 & 32.8 & 41.3 & \SW{75.8} & 40.7 & \SW{48.3}   \\% &  23.4 \\
    \system{DM}             & 35.4 & 49.3  & 45.2 & 29.7 & 37.1 & \SW{60.0} & 37.8 & 42.8 \\ % & 22.6\\
    \system{ADM}           & 36.1 & 53.5  & 48.0 & 32.0 & 41.1 & 72.1 & 39.5 & 47.1\\% & 23.3 \\
    \revision{\system{FT Res}}     & 37.5 & \SW{55.7}  & \SW{51.1}   & 33.1   &  \SW{44.1}  & \SW{86.7} & 41.6 & \SW{51.4}\\%  & \SW{21.2} \\
    \system{MDL Res}     & 37.3 & 55.5  & \SW{50.2}   & \SW{32.2}   &  \SW{42.1}  & \SW{86.7} & 41.2 & \SW{50.7}\\%  & \SW{21.2} \\
    \system{WDCMT}       & 35.6 & 53.1 & 48.4 & 30.5 & \SW{37.7} & \SW{56.0} & 38.5 & 43.6 \\ % & 20.4 \\ 
    \hline
  \end{tabular}
  \caption{Translation performance with automatic domains, computed with the original test sets. Significancy tests are for comparisons with the 6-domain scenario \revision{(Table~\ref{tab:performance}).}}
  \label{tab:subdomains}
  \fyDone{Fill the table with correct results,}\fyDone{Change wavg and avg}
\end{table*}

@@

% include your own bib file like this:
% \bibliographystyle{coling}
\bibliographystyle{acl_natbib}
\bibliography{multidomain}

\newpage\newpage
\section*{Appendices}

\subsection*{A - Description of multi-domain systems \label{ssec:implementation-details}}
\revision{%
The systems used in this study are set up as follows:
\begin{itemize}
\item \system{Mixed-NAT}, \system{FT-full}, \system{TTM}, \system{DC-Tag} use the a medium Transformer model of \cite{Vaswani17attention} with the following settings: embeddings size and hidden layers size are set to~512. Multi-head attention comprises 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. 
% The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
Training use a batch size of~12,288 tokens; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.
\item \system{FT Res} and \system{MDL res} use the same medium Transformer model, and add residual layers with a bottleneck dimension of size 1024.
  % \cite{Bapna19simple} showed that if the bottleneck dimension is large enough, the gap between \system{FT-block} and \system{FT-full} will be small.\fyTodo{This comment is confusing}.
\item \system{ADM}, \system{DM} use medium Tranformer model and a domain classifier composing of 3 dense layers of size $512 \times 2048$, $2048 \times 2048$ and $2048 \times domain\_num$. The two first layers of the classifier use the $\operatorname{ReLU}()$ as activation function, the last layer uses $\tanh()$ as activation function.
\item \system{DC-Feat} uses medium Transformer model and domain embeddings of size 4. Given a sentence of domain~$i$ in a training batch, the embedding of domain $i$ is concatenated to the embedding of each token in the sentence.
\item \system{LDR} uses medium Transformer model and for each token we introduce a \system{LDR} feature of size $4 \times domain\_num$. Given a sentence of domain $i\in[1,..,K]$ in the training batch, for each token of the sentence, the \system{LDR} units of the indexes outside of the range $[4(i-1),..,4i-1]$ are masked to 0, the masked LDR feature will be concatenated to the embedding of the token. Details are in \cite{Pham19generic}.
\item \system{Mixed-NAT-RNN} uses one layer LSTM bidirectional as encoder and one layer LSTM as decoder. The size of each hidden layer is 1024, the size of word embeddings is 512. 
\item \system{WDCNMT} uses one layer GRU bidirectional as encoder and one layer GRU-conditional as decoder. The size of each hidden layer is 1024, the size of word embedding is 512.
\end{itemize}
\paragraph{Training} For each domain, we create train/dev/test sets by randomly each corpus. We maintain the size of validation sets and of test sets equal to 1,000 lines for every domain.
The learning rate is set
% to $lr = d_{model}^{-0.5}*\min(step\_num^{-0.5},step\_num * warmup\_steps^{-1.5})$ where $d_{model}=512$,$warmup\_steps=4000$,
as in \cite{Vaswani17attention}. For the fine-tuning procedures used for \system{FT-full} and \system{FT Res}, we continue training using the same learning rate schedule, continuing the incrementation of the number of steps. All other MDMT systems reported in Tables~\ref{tab:performance} and \ref{tab:redomains} use a combined validation set comprising 6,000 lines, obtained by merging the six development sets. For the results in Table~\ref{tab:warmrestart} we also append the validation set of \domain{news} to the multi-domain validation set. In any case, training stops if either training reaches the maximum number of iterations (50,000)\fyDone{How many ?} or the score on the validation set does not increase for three consecutive evaluations. We average five checkpoints to get the final model.\fyDone{up to the best ?}
}
\end{document}

>>>>

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
    \system{Mixed-Nat}  \hfill{\footnotesize[65m]} & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
    \system{Mixed-Bal}   \hfill{\footnotesize[65m]} &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 \\ %& \\
    \system{FT-Full}       \hfill{\footnotesize[6$\times$65m]} & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & \SB{42.7} & \SB{53.8} \\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag} \hfill{\footnotesize[+4k]}        & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & \SB{80.5} &41.6 & 50.1    \\%    & 21.8 \\
    \system{DC-Feat} \hfill{\footnotesize[+140k]}    & 37.7  & 54.9 & 49.5   & 32.9 & 43.6 & \SB{79.9} &41.4 & 49.9   \\% & \SW{21.7} \\
    \system{LDR}       \hfill{\footnotesize[+1.4m]}    & 37.0   & 54.7 & 49.9 & 33.9 & 43.6 & \SB{79.9} &40.9 & 49.8          \\% & 22.1 \\ 
    \system{TTM}      \hfill{\footnotesize[+4k]}        & 37.3 & 54.9 & 49.5 & 32.9 & 43.6 & \SB{79.9} &41.0 & 49.7     \\% &  23.4 \\
    \system{DM}        \hfill{\footnotesize[+0]}         & \SW{35.6} & \SW{49.5}  & \SW{45.6}& \SW{29.9} & \SW{37.1} & \SW{62.4} & 38.1 & 43.4 \\ % & 22.6\\
    \system{ADM}      \hfill{\footnotesize[+0]}         & 36.4 & \SW{53.5}  & \SW{48.3} & \SW{32.0} & \SW{41.5} & \SW{73.4} & 38.9 & 47.5 \\% & 23.3 \\
    \revision{\system{FT-Res}}   \hfill{\footnotesize[+12.4m]}  & 37.3 & \SB{57.9} & \SB{53.9} & 33.8 & \SB{46.7} & \SB{90.2}  & \SB{42.3} & \SB{53.3} \\ % & 20.5\\ \hline
    \system{MDL-Res} \hfill{\footnotesize[+12.4m]}    & 37.9 & \SB{56.0}  & \SB{51.2}   & 33.5   &  44.4  & \SB{88.3} & 42.0 & \SB{51.9} \\%  & \SW{21.2} \\
%     \hfill MDL Res (gen)    & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline \hline
    \system{Mixed-Nat-RNN}  & 36.8 & 53.8 & 47.2 & 30.0 & 35.7 & 60.2  & 39.2  & 44.0 \\
    \hline
    \system{WDCMT}       & 36.0 & 53.3 & \SB{48.8} & 31.1 & \SB{38.8} & \SW{58.5} & 39.0 & 44.4 \\ % & 20.4 \\
    \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems \revision{based on the same Transformer (top) or RNN (bottom) architecture. The former contains 65m parameters, the latter has ???. For each system, we report the number of domain specific parameters,}  BLEU scores for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. \revision{In the former case, we take the domain proportions from Table~\ref{tab:Corpora}}. Boldface denotes significant gains with respect to \system{Mix-Nat} (or \system{Mix-Nat-RNN}, for WDCMT), underline denotes significant losses.}
  \label{tab:performance}
  % \fyDone{Fill the table with all results, including a comparison with *RNNs* for wcmd}
  \fyDone{Do we have significancy tests for averages?} %\fyTodo{Add tests wrt to RNN}
\end{table*}

@@

\begin{table*}
  \centering% \small
  \begin{tabular}{|p{1.8cm}|*{10}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & \multicolumn{2}{c|}{Wrong} \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{law} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} &  \multicolumn{1}{c|}{\domain{rnd}} &  \multicolumn{1}{c|}{\domain{new}}\\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_2$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law}   & \domain{all} & \domain{News} \\
    \system{FT-Full}      & -0.1 & -0.6 & \SW{-1.5} & -0.2& \SW{-2.3} & \SW{-5.1} &\SW{-1.6} & \SW{-1.4}& \SW{-19.6} & \SW{-3.3}\\% [32.5]
    \system{DC-Tag}     & -0.2 & -0.3& +\SB{0.1}  & +0.2& -0.4 & -0.4 & -0.5 & -0.4 & \SW{-13.4} & \SW{-1.7}\\% [35.9]
    \system{DC-Feat}    & -0.5 & 0.0 & +\SB{0.3}   & +0.3 & +0.3 & +0.3 & 0.3 & +0.1 & \SW{-14.2} &\SW{-1.8}\\ % [34.9] 
    \system{LDR}           & +0.1 & +0.1 & +0.4 & +0.4 & 0.0 &  0.0 &  0.0 & +0.1& \SW{-12} & \SW{-1.4}\\ % [37.0]
    \system{TTM} (*)        & -0.2 &  -0.2 & -0.2 & -0.2 & -0.3 &-0.3 &  0.0 & -0.3 & 0.0 & -0.1\\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{DM} (*)           & -0.3   & -0.3  & +0.4 & +0.4 & +0.3 & +0.3 & +0.9 & +0.1 & 0.0 &-0.9\\
    \system{ADM} (*)        & +0.6   & +0.6 & +0.4 & +0.4 & +0.4 & +0.4 &  +0.1 & -0.4 & 0.0&-0.2\\
    \revision{\system{FT-Res}}   & -0.1   & -0.4 & -0.3 &-0.3 & \SW{-2.2} & \SW{-2.9} & \SW{-2.4} & -\SW{3.2} & \SW{-13.3} & \SW{-3.0}\\ % [31.8]
    \system{MDL-Res}   & -0.2   & -0.1 & +\SB{0.2} &+0.0 & -0.9 & -0.9 & +0.7 & -0.3 & \SW{-18.6} & \SW{-1.3}\\ % [31.8]
    \system{WDCMT} (*)     & -0.0    & -0.0  & +0.2 & +0.2  & +0.8 & +0.8  & -0.4 & -0.8 & 0.0 & +0.2 \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. In the Split/Merge experiments, we report BLEU differences for the related test set(s). Underline denotes significant loss when domains are changed wrt.\ the baseline situation; bold for a significant improvement over \system{FT-Full}; (*) tags systems ignoring test domains.
    \fyDone{Check wrong and significance of diff for ``old''}\fyDone{How about wrong ?}
  }
  \label{tab:redomains}
\end{table*}

@@

%    \system{WDCMT}     &&&&&&& & &\\[-2pt]
%                    &&&&&&&&& \\
    \footnotesize \revision{\system{FT-Res}}  & 37.0 & 57.6 & 53.8 & 34.5 &	46.1 & 91.1 & 29.6 &	42.2  & 53.3 \\[-2pt]
                               & \sbcl{+0.3}{+0.3} & \sbcl{+0.4}{+0.4} & \sbcl{+0.1}{+0.1} & \sbcl{-0.7}{-0.7} & \sbcl{+0.5}{+0.5} & \sbcl{-0.9}{-0.9} & \sbcl{\SW{-9.0}}{-0.6} & \sbcl{-0.1}{-0.1} & \sbcl{+0.2}{+0.2} \\

@@

\subsection{Automatic domains \label{ssec:autodomains}}
In this section, we experiment with automatic domains, obtained by clustering sentences into $k=30$ classes using the k-means algorithm based on generic sentence representations obtained via mean pooling as in Section~\ref{ssec:corpora}. This allows us to evaluate requirement [P7-scale], training and testing our systems as if these domains were fully separated. Many of these clusters are mere splits of the large \domain{med}, while a fewer number of classes are mixtures of two (or more) existing domains \revision{(details are in Appendix B)}. We are thus in a position to reiterate, at a larger scale, the measurements of Section~\ref{ssec:redomains} and test whether multi-domain systems can effectively take advantage from the cross-domain similarities and to eventually perform better than fine-tuning. \revision{The results in Table~\ref{tab:avg_automatic_domains} suggest that MDMT actually can surpass fine-tuning for the smaller clusters, especially for small subsets of the medical domain; for the large clusters, this is no longer true.}

@@

\begin{table*}[t]
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}} \hline
%     &&&&&& \\
    Domain / Model  & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline % & \multicolumn{1}{c|}{\domain{news}} 
  %    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 \\% & 23.5\\
  %     \system{FT-Full}       & 37.7 & \SB{59.2} & \SB{54.5} & 34.0 & \SB{46.8} & \SB{90.8}   & 42.8 & 53.8\\
  %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.5 & \SW{54.0} & 49.0   & 33.6 & \SW{42.2} & \SW{76.7} & 41.6 & 49.0 \\%    & 21.8 \\
    \system{DC-Feat}      & 37.3  & 54.2 & 49.3   & 33.6 & \SW{41.9} & \SW{75.8} & 40.8 & \SW{48.7}  \\% & \SW{21.7} \\
    \system{LDR}             & 37.4   & 54.1 & \SW{48.7} & \SW{32.5} & \SW{41.4} & \SW{75.9} & 39.1 & \SW{48.3}         \\% & 22.1 \\ 
    \system{TTM}            & 37.4 & \SW{53.7} & 48.9 & 32.8 & 41.3 & \SW{75.8} & 40.7 & \SW{48.3}   \\% &  23.4 \\
    \system{DM}             & 35.4 & 49.3  & 45.2 & 29.7 & 37.1 & \SW{60.0} & 37.8 & 42.8 \\ % & 22.6\\
    \system{ADM}           & 36.1 & 53.5  & 48.0 & 32.0 & 41.1 & 72.1 & 39.5 & 47.1\\% & 23.3 \\
    \revision{\system{FT-Res}}     & 37.5 & \SW{55.7}  & \SW{51.1}   & 33.1   &  \SW{44.1}  & \SW{86.7} & 41.6 & \SW{51.4}\\%  & \SW{21.2} \\
    \system{MDL-Res}     & 37.3 & 55.5  & \SW{50.2}   & \SW{32.2}   &  \SW{42.1}  & \SW{86.7} & 41.2 & \SW{50.7}\\%  & \SW{21.2} \\
    \system{WDCMT}       & 35.6 & 53.1 & 48.4 & 30.5 & \SW{37.7} & \SW{56.0} & 38.5 & 43.6 \\ % & 20.4 \\ 
    \hline
  \end{tabular}
  \caption{Translation performance with automatic domains, computed with the original test sets. Significancy tests are for comparisons with the 6-domain scenario \revision{(Table~\ref{tab:performance}).}}
  \label{tab:subdomains}
  \fyDone{Fill the table with correct results,}\fyDone{Change wavg and avg}
\end{table*}

@@

% include your own bib file like this:
% \bibliographystyle{coling}

% \newpage\newpage
\section*{Appendices}

\subsection*{A - Description of multi-domain systems \label{ssec:implementation-details}}
\revision{%
The systems used in this study are set up as follows:
\begin{itemize}
\item \system{Mixed-NAT}, \system{FT-full}, \system{TTM}, \system{DC-Tag} use the a medium Transformer model of \cite{Vaswani17attention} with the following settings: embeddings size and hidden layers size are set to~512. Multi-head attention comprises 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells. 
% The gated variant is made of a dense layer, followed by a layer normalization and a sigmoid activation.
% The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.
Training use a batch size of~12,288 tokens; optimization uses Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$ and Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ for all layers.
\item \system{FT-Res} and \system{MDL-res} use the same medium Transformer model, and add residual layers with a bottleneck dimension of size 1024.
  % \cite{Bapna19simple} showed that if the bottleneck dimension is large enough, the gap between \system{FT-block} and \system{FT-full} will be small.\fyTodo{This comment is confusing}.
\item \system{ADM}, \system{DM} use medium Tranformer model and a domain classifier composing of 3 dense layers of size $512 \times 2048$, $2048 \times 2048$ and $2048 \times domain\_num$. The two first layers of the classifier use the $\operatorname{ReLU}()$ as activation function, the last layer uses $\tanh()$ as activation function.
\item \system{DC-Feat} uses medium Transformer model and domain embeddings of size 4. Given a sentence of domain~$i$ in a training batch, the embedding of domain $i$ is concatenated to the embedding of each token in the sentence.
\item \system{LDR} uses medium Transformer model and for each token we introduce a \system{LDR} feature of size $4 \times domain\_num$. Given a sentence of domain $i\in[1,..,K]$ in the training batch, for each token of the sentence, the \system{LDR} units of the indexes outside of the range $[4(i-1),..,4i-1]$ are masked to 0, the masked LDR feature will be concatenated to the embedding of the token. Details are in \cite{Pham19generic}.
\item \system{Mixed-NAT-RNN} uses one layer LSTM bidirectional as encoder and one layer LSTM as decoder. The size of each hidden layer is 1024, the size of word embeddings is 512. 
\item \system{WDCNMT} uses one layer GRU bidirectional as encoder and one layer GRU-conditional as decoder. The size of each hidden layer is 1024, the size of word embedding is 512.
\end{itemize}
\paragraph{Training} For each domain, we create train/dev/test sets by randomly each corpus. We maintain the size of validation sets and of test sets equal to 1,000 lines for every domain.
The learning rate is set
% to $lr = d_{model}^{-0.5}*\min(step\_num^{-0.5},step\_num * warmup\_steps^{-1.5})$ where $d_{model}=512$,$warmup\_steps=4000$,
as in \cite{Vaswani17attention}. For the fine-tuning procedures used for \system{FT-full} and \system{FT-Res}, we continue training using the same learning rate schedule, continuing the incrementation of the number of steps. All other MDMT systems reported in Tables~\ref{tab:performance} and \ref{tab:redomains} use a combined validation set comprising 6,000 lines, obtained by merging the six development sets. For the results in Table~\ref{tab:warmrestart} we also append the validation set of \domain{news} to the multi-domain validation set. In any case, training stops if either training reaches the maximum number of iterations (50,000)\fyDone{How many ?} or the score on the validation set does not increase for three consecutive evaluations. We average five checkpoints to get the final model.\fyDone{up to the best ?}
}
